---
name: "Migrant Module Intermediate"
author: "HIV Platform tool"
title: "Infections among migrants prior and post arrival at the country of destination"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_fragment:
    number_sections: no
    smart: yes
    fig_caption: yes
params:
  Missingness: NA
editor_options:
  chunk_output_type:console
---
```{r setup, include = FALSE}
require(hivPlatform, quietly = TRUE)
knitr::opts_chunk$set(
  echo = FALSE, results = "asis", message = FALSE, warning = FALSE, include = TRUE
)
```

## 1. Overview

CAUTION:

Estimates of the time of infection require the following variables: Sex, transmission category,
Region of Origin, AIDS diagnosis. CD4 count and VL are used if available. In addition, the time of
infection must be compared to the arrival time and the estimation based on the cases for which both
Year of Arrival and Year of Diagnosis are known.

It is possible to run the migration estimation on the original dataset, but it is recommended to
use the imputation first.

The estimation is performed for adults only.

Cases excluded due to missing values:

```{r, eval = TRUE}
knitr::kable(
  params$Missingness,
  align = rep('r', ncol(params$Missingness)),
  col.names = c('Missing variable', 'Number of excluded cases')
)
```

## 2. Description of data used in estimation


## 3. Estimates of the proportion of the migrants infected prior and post arrival
